---
title: "Code Book"
output: html_document
---
```{r, echo=FALSE}
wearables = read.table("Wearables_summary.txt", header= TRUE)
```
## 


##Variables 

Description of variables in the dataset is pulled from the `features_info.txt` file from the original dataset (https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip )

> The features selected for this database come from the accelerometer and gyroscope 3-axial raw signals tAcc-XYZ and tGyro-XYZ. These time domain signals (prefix 't' to denote time) were captured at a constant rate of 50 Hz. Then they were filtered using a median filter and a 3rd order low pass Butterworth filter with a corner frequency of 20 Hz to remove noise. Similarly, the acceleration signal was then separated into body and gravity acceleration signals (tBodyAcc-XYZ and tGravityAcc-XYZ) using another low pass Butterworth filter with a corner frequency of 0.3 Hz. 

> Subsequently, the body linear acceleration and angular velocity were derived in time to obtain Jerk signals (tBodyAccJerk-XYZ and tBodyGyroJerk-XYZ). Also the magnitude of these three-dimensional signals were calculated using the Euclidean norm (tBodyAccMag, tGravityAccMag, tBodyAccJerkMag, tBodyGyroMag, tBodyGyroJerkMag). 

> Finally a Fast Fourier Transform (FFT) was applied to some of these signals producing fBodyAcc-XYZ, fBodyAccJerk-XYZ, fBodyGyro-XYZ, fBodyAccJerkMag, fBodyGyroMag, fBodyGyroJerkMag. (Note the 'f' to indicate frequency domain signals). 

> These signals were used to estimate variables of the feature vector for each pattern:  
'-XYZ' is used to denote 3-axial signals in the X, Y and Z directions.

The std and mean suffixes on the variables indicate calculation of mean and standard deviation, respectively. Additionally, the variable `activity`, the type of activity being performed during measurement, and `subject`, the individual subject (represented by a number ranging from 1-30) performing the activity, are included. 

The full list of variables is : 

```{r}
colnames(wearables)
```

## Dataset transformations

The R script `run_analysis.R` :

1.  Reads in both the training and testing datasets.
2.  Reads in column labels for the datasets and renames columns based on those labels.
3.  Reads in supporting datasets, including activity labels and subject numbers for both the training and testing datasets and merges those columns with the training and testing datasets.
3.  Joins the training and testing datasets.
4.  Selects only columns with mean and standard deviation values.
5. Converts activity numbers to activity names
6. Creates a summary dataset with average of each variable for each activity and each subject.
7. Writes the summary dataset to file. 
